Checkpoint 4

### 2020-04-28 Checkpoint 4.Rmd
quinn plots more stuff

---
title: "Checkpoint 4"
author: "Will Madairy, Sofia Pozsonyiova, Quinn Rafferty, Federico Chung"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
header-includes:
  - \usepackage{tabularx}
output:
  pdf_document: default
  html_document: default
abstract: ""
---

>>>>

---
title: "Checkpoint 4"
author: "Will Madairy, Sofia Pozsonyiova, Quinn Rafferty, Federico Chung"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
header-includes:
  - \usepackage{tabularx}
output:
  pdf_document: default
  html_document: default
---

```{r, warning=FALSE}
library(dplyr)
library(usmap)
library(maps)
library(ggplot2)
library(tidyverse)
library(ggmap)
library(viridis)
library(rgdal)
library(gridExtra)
library(plotly)
require(janitor)
require(reshape2)
require(tidyr)
require(rstan)
require(rstanarm)
require(bayesplot)
```

# Quinn plots stuff
```{r}
a<- ggplot(Finaldata, aes(x = ChinaVirusInterest, fill = as.factor(State))) + 
  geom_density(alpha = 0.5)+ ggtitle("China Virus Density by State")

b<- ggplot(Finaldata, aes(x = Day, y = ChinaVirusInterest, color = factor(State))) + 
    geom_point() + 
    geom_smooth(method = "lm", se = FALSE) + 
    facet_wrap(~ State) + 
    theme(legend.position = "right")+
    ggtitle("China Virus Interest by Day by State")

c<- ggplot(Finaldata, aes(x = ChinaVirusInterest, color = factor(StateColor))) + 
    geom_histogram() + 
    facet_wrap(~ Winner) +
    theme(legend.position = "right") + 
    scale_colour_manual( values=c("red"= "red3", "blue"= "royalblue", "purple"="darkorchid3")) +
    ggtitle("China Virus Google by State Poltical Party Winner")

d <-  ggplot(Finaldata, aes(y=positive, x=Winner, fill=(Winner)))+
      geom_boxplot() +
      facet_wrap(~Region)+
      theme(legend.position = "none") +
      scale_fill_manual(values = c("Democrat"="blue3", "Republican"= "red3"))+
      lims(y= c(0,1000))+
      ggtitle("Positive COVID-19 Cases by State Political Party Winner & Region")

ggplotly(a)
ggplotly(b)
ggplotly(c) #Shows that Democrat states tend to have a higher interest in Googling China Virus 
ggplotly(d)
```
